% Ubah judul dan label berikut sesuai dengan yang diinginkan.
\section{Introduction}
\label{sec:introduction}

% Ubah paragraf-paragraf pada bagian ini sesuai dengan yang diinginkan.
There are three main parts of Mobile Robot, namely Sensor, Control, and Actuator. All the main parts are connected to each other. Sensor is used to detect the environment around the robot. Control is used to process the data from the sensor and decide the next action. Actuator is used to execute the action that has been decided by the control.  
 
There is a sensor for Mobile Robot that can sense 360 degree around the robot. The sensor is called Omnivision Camera. The use of Omnivision Camera give more benefits because it can grab the information around robot with only one capture. The basic concept of Omnivision Camera is to use a mirror to reflect the environment around the robot. The mirror is placed in front of the camera. The camera is placed in the middle of the mirror and projected 90 degree to the ground of Robot. Not only can sense the environment around the robot, the camera can also sense within 10m distance. 

The hardware installation process of Omnivision Camera is hard. There are a common mistakes that everyone can accpet it such as misplaced camera, misplaced mirror, bad mirror, misplaced the whole system, and many more. Errors like that can cause a bad representation of the environment around the robot. The bad representation of the environment can cause the robot to make a wrong decision. 